---
title: "Flashcard Package Functions"
author: "Alex"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



This document will carry the functions that will eventually be used in my created package for the R programming class.

## Flashcard Input
This first function is used to enter in the flashcard data into a data frame for use later on.

```{r}
flashcards <- function() {
  flashcards_data <- data.frame(
    question = character(),
    answer = character(),
    correct = integer(),
    total = integer(),
    stringsAsFactors = FALSE
  )

  main_menu <- function() {
    repeat {
      choice <- menu(c("Add Flashcards", "Study Flashcards", "View Progress", "Exit"), title = "Flashcard Program Menu")
      switch(choice,
             add_flashcards(),
             study_flashcards(),
             view_progress(),
             break)
    }
  }
```

## Menu
This second function can be used to select any of the various functions that will eventually be built for the project.
```{r}
  
  main_menu <- function() {
    repeat {
      choice <- menu(c("Add Flashcards", "Study Flashcards", "View Progress", "Exit"), title = "Flashcard Program Menu")
      switch(choice,
             add_flashcards(),
             study_flashcards(),
             view_progress(),
             break)
    }
  }

```

 ## Add Flashcards
 This function will allow the user to input flashcards for use.
```{r}
add_flashcards <- function() {
  repeat {
    question <- readline(prompt = "Enter the flashcard question (or press ENTER to stop adding): ")
    if (nchar(question) == 0) break

    answer <- readline(prompt = "Enter the flashcard answer: ")
    flashcards_data <<- rbind(flashcards_data, data.frame(question = question, answer = answer, correct = 0, total = 0, stringsAsFactors = FALSE))
  }
}

```
 
## Study Flashcards
This function allows user to study flashcards they input earlier.
```{r}
  study_flashcards <- function() {
    if (nrow(flashcards_data) == 0) {
      cat("No flashcards available to study. Please add some flashcards first.\n")
      return()
    }

    repeat {
      index <- sample(1:nrow(flashcards_data), 1)
      question <- flashcards_data$question[index]
      answer <- flashcards_data$answer[index]

      cat("Question: ", question, "\n")
      user_answer <- readline(prompt = "Your answer: ")

      if (tolower(user_answer) == tolower(answer)) {
        cat("Correct!\n\n")
        flashcards_data$correct[index] <<- flashcards_data$correct[index] + 1
      } else {
        cat("Incorrect. Correct answer is: ", answer, "\n\n")
      }
      flashcards_data$total[index] <<- flashcards_data$total[index] + 1

      choice <- readline(prompt = "Do you want to continue studying? (yes/no): ")
      if (tolower(choice) != "yes") break
    }
  }

```

## View Progress
This function allows the user to view their progress.
```{r}
  view_progress <- function() {
    if (nrow(flashcards_data) == 0) {
      cat("No flashcards available. Please add some flashcards first.\n")
      return()
    }

    cat("\nFlashcard Progress:\n")
    for (i in 1:nrow(flashcards_data)) {
      cat(sprintf("%s: %d correct out of %d attempts\n",
                  flashcards_data$question[i],
                  flashcards_data$correct[i],
                  flashcards_data$total[i]))
    }
    cat("\n")
  }

  main_menu()
}

```

